\section{Overview}

\begin{multicols}{2}

% The x-IMU3 is x-io Technologies' third generation \ac{IMU}.
% It is a high-performance and versatile measurement device designed to accommodate a wide range of data logging and real-time applications including biomechanics, motion-capture, virtual reality, drones, robotics, and industrial.
Thetis is a nine \ac{DOF} \ac{IMU} that is capable of reporting the acceleration, rotation rate, orientation, and position of a body.
It was developed as part of a thesis project for the Ocean Engineering Department at the Florida Institute of Technology.
The device is designed to be used in classroom and laboratory environments or out in the field, wherever inertial data logging is desired.

Thetis can communicate with a host computer over a \acs{USB} or Wi-Fi connection, streaming data in real-time to an operator.
For more embedded applications, Thetis has an on-board battery and \acs{microSD} card storage, allowing it to remotely data log without an operator.
A simple user interface allows for a single operator to deploy Thetis in any condition.

\textbf{Sensors}
\begin{itemize}[nolistsep]
    \item Gyroscope, \textpm{}2000\textdegree{}/s, 100 Hz
    \item Accelerometer, \textpm{}32 g, 100 Hz
    \item Magnetometer, \textpm{}16 gauss, 100 Hz
\end{itemize}

\textbf{Calibration}
\begin{itemize}[nolistsep]
    \item 15-parameter calibration for: axis sensitivity, axis offset, inter-axis misalignment, and package misalignment.
    \item Hard-iron and soft-iron calibration
    \item On-board gyroscope bias correction algorithm
\end{itemize}

\textbf{\acs{AHRS}}
\begin{itemize}[nolistsep]
    \item Algorithm outputs:
    \begin{itemize}
        \item Quaternion
        \item Rotation matrix\footnote{Supported, but not yet implemented.}
        \item Euler angles
        \item Linear acceleration\footnotemark[\value{footnote}]
        \item Earth acceleration\footnotemark[\value{footnote}]
    \end{itemize}
    \item Linear acceleration rejection\footnotemark[\value{footnote}]
    \item Magnetic distortion rejection\footnotemark[\value{footnote}]
    \item 100 Hz update rate
    \item Static accuracy:
        \begin{itemize}
            \item 0.5\textdegree{} \acs{RMS} inclination\footnote{Remains to be validated.}
            \item 1\textdegree{} \acs{RMS} heading\footnotemark[\value{footnote}]
        \end{itemize}
\end{itemize}

\columnbreak

\textbf{Communication}
\begin{itemize}[nolistsep]
    \item \acs{USB} (\acs{CDC})
    \item \acs{TCP} (Wi-Fi)\footnotemark[\numexpr\value{footnote}-1\relax]
    \item \acs{UDP} (Wi-Fi)
\end{itemize}

\textbf{Wi-Fi}
\begin{itemize}[nolistsep]
    \item Client and \acs{AP} mode
    \item Single band (2.4 GHz)
    \item WPA/WPA2-Personal
\end{itemize}

\textbf{Data logging}
\begin{itemize}[nolistsep]
    \item Supports \acsp{microSD} up to 32 GB\footnote{The product is supplied with an 4 GB \acs{microSD} that can be upgraded by the user.}
    \item Start/stop logging remotely\footnotemark[\numexpr\value{footnote}-2\relax]
    \item Start/stop logging with physical button
    \item USB download\footnote{USB downloading is currently in development and not yet supported.}
    \item Wi-Fi download\footnote{Wi-Fi downloading is currently in development and not yet supported.}
    \item \acs{CSV} output
\end{itemize}

\textbf{Battery}
\begin{itemize}[nolistsep]
    \item Internal battery charged by \acs{USB}
    \item 9 hours data logging\footnote{Estimated}
    \item 4 hours Wi-Fi client\footnote{Estimated, assuming constant transmission.}
\end{itemize}

\textbf{Housing}
\begin{itemize}[nolistsep]
    \item \acs{IP67}
    \item Chassis mount via two M3 screws or bolts
\end{itemize}

\textbf{Software \acs{GUI}}
\begin{itemize}[nolistsep]
    \item Connect to multiple xio-compatible \acsp{IMU} (e.g. x-IMU3, Thetis)
    \item Real-time data graphs and 3D view
    \item Log data to \acs{CSV}
    \item Windows, macOS, Ubuntu
\end{itemize}

\textbf{Software \acs{API}}
\begin{itemize}[nolistsep]
    \item Rust, C, C++, C\#, Python
    \item Code examples for other languages available
\end{itemize}

\end{multicols}

\clearpage
